Alleviating the Topology Mismatch Problem in Distributed Overlay Networks: A Survey

### 2015-09-26 journals/jss/rebuttal/rebuttal.tex

\documentclass[10pt,letterpaper]{article}

\usepackage{color}
\usepackage[margin=3cm, a4paper]{geometry}
\usepackage[hyphens]{url}
\usepackage{paralist}

\setlength{\parindent}{0pt}
\setlength{\parskip}{5pt}

\begin{document}

\title{
	\textbf{\textsf{
	Revised Manuscript JSS-D-15-00624\\
	Authors' Responses to the Reviewers' Comments
	}}
}
\author{Vassilis Moustakas, H\"useyin Akcan, Mema Roussopoulos, and Alex Delis}
\maketitle

% Introduction
\section*{}
We would like to thank the reviewers for their comments and recommendations 
that helped us a lot while revising our manuscript.

In this new version of our survey, 
we have attempted to address all feasible comments 
and sufficiently answer all pertinent questions.
As a consequence, the 
manuscript has undergone a number 
of important changes and updates, which are:

\begin{enumerate}

\item 
Section 2.3 has been revised to offer more accurate definitions 
of the evaluation criteria ``efficiency'' and ``overhead'' that 
better distinguish the two and more accurately articulate
their distinct purpose in our evaluation.
\item 
We have added timeline figures for unstructured and structured families 
of approaches to depict
the temporal and trending characteristics of applied methodologies.
\item 
Sections 3.2 and 4.2 have been updated with discussion and comments 
that address aspects of the timeline figures.
\item 
Mini-tables have been updated to include 
algorithm names throughout the text. 
\item 
Figures of pages 19-21 and 32-34 have been updated to indicate 
the year next to the algorithm name.

\end{enumerate}

In the following two segments, we provide detailed replies to 
the comments and questions raised by the reviewers. 
Each individual comment has been copied \emph{as-is} from 
the original decision letter that was sent to us by 
the Editor--in-Chief followed by our corresponding response.

% Responses to the First Reviewer
\clearpage
\subsection*{\textbf{\textsf{Responses to the First Reviewer}}}

%%R1,C1
\subsubsection*{\textbf{\textsf{Reviewer's Comment\#1}}}
\noindent
\emph{I have a minor comment to make to improve the quality of the paper. Most of
the evaluation is carried out in a ``descriptive'' way, which is fine by me.
However it would be interesting to see some experimental evaluation (for at least
one of the metrics, e.g. efficient) using various data sets. I understand this
could be a lot of work, however if you could focus on three systems and test
efficiency/scalability, the results would be more convincing. These also will
support the claims you have made.}\\[6pt]

\noindent
\textbf{\textsf{Response}}:
%%
We would like to thank the reviewer for the thoughtful suggestion. 
It would have been indeed 
both an exciting and tremendous exercise 
to put all surveyed approaches under a \emph{common experimental setting} 
(to the extent possible) 
and test them against diverse workloads.

As the reviewer has kindly pointed out, this would have 
translated to an excessive amount of effort with rather uncertain results. 
More importantly, such an
effort would have yielded not a survey-type manuscript ---our 
stated objective--- but rather something much more resembling 
to an experiment-based monograph. 
Frankly, we never considered going into this level of evaluation 
work for the numerous details and diverse points of the algorithms 
would have posed insurmountable levels of challenge.

We believe that the suggestion of picking $3$ (three)
out of the $N$ approaches presented and evaluating
them quantitatively has important practical difficulties and 
does not guarantee added value to the surveyed material.

For example, what would be the methodology used to pick those
three systems? Does one choose three at random, 
the three most popular/widely deployed or
the ``best'' three w.r.t. the metric of interest, 
based on our prediction of which we think will
fare best? 
Does one choose the three that are simplest to implement?

There are reasons for and against following each of the 
above selection approaches and this apparently non-systematic approach makes
it unclear whether presenting results for just three of 
the surveyed approaches would render much added value
to our survey manuscript.

Enabling comparison through developing functional prototypes and subsequent 
quantitative evaluation would have been truly an undertaking of 
enormous dimensions. 
Not only do we lack pertinent resources, but also 
performing a fair and complete comparison would be arguably 
beyond the scope of this survey.

Although we have clearly given the reviewer's comment
the due consideration, for all the above reasons, it would have been 
unfair for the manuscript and its carefully crafted balance in 
presenting a trove of approaches to venture in such an experimental  direction. 
We do appreciate the comment however and we are thankful for the positive 
overall evaluation of our survey.

% Responses to the Third Reviewer
\clearpage
\subsection*{\textbf{\textsf{Responses to the Third Reviewer}}}

%% R3.C1
\subsubsection*{\textbf{\textsf{Reviewer's Comment\#1}}}
\noindent
\emph{I do recommend changing terminologies to highlight the differences between
``efficiency'' and ``overhead''. Maybe instead you can use
``Topology adaptation cost'' instead of efficiency, and break overhead into both
``Topology maintenance cost'' and ``Communication overhead''. Again this is just a
recommendation, mainly to clarify the underlying differences between what is meant
by efficiency and overhead.}\\[6pt]

\noindent
\textbf{\textsf{Response}}:
Thank you for this suggestion.

Although a potential change of the 
term ``Efficiency'' to ``Topology Adaptation Cost''
followed by a break up of the term 
``Overhead'' to ``Topology Maintenance Cost'' and ``Communication Overhead''
would have been feasible, we believe that such modifications would ultimately 
render the way the overall text has been written somewhat problematic.

In particular, we use the term ``Efficiency'' to identify how \emph{closely matched} are the
overlay and underlying networks after applying a specific approach. 
We experience good efficiency when few(er) packets travel across the network
while at the same time, an approach can preserve 
discoverability of resources (not reducing the search scope). 
In this context, ``Topology Adaptation Cost'' is intended to describe something 
different (as stated below).

We use the ``Overhead'' term to quantify the (mainly communication) cost
that a given approach carries when applied, to (i) create, (ii) adapt and (iii) maintain
the topology awareness of the P2P network.

The proposed distinction of
``Topology Maintenance Cost'' and ``Communication Overhead'' is, for this reason, not
accurate as it is not complete in terms of the intented abstraction of the measure we
want to use in this context.  
``Communication Cost'' can be thought of as an all encompassing cost 
that includes ``Topology Maintenance Cost'' (added communication to maintain topology
awareness in the presence of network churn).

The above choice also may clarify our intention to have
``Topology Adaptation Cost'' fall into the ``Overhead'' family of measures and
not in ``Efficiency'' as suggested by the reviewer above.

Having (hopefully successfully) argued for the use of terms as they appeared in the 
first version of the manuscript, we also understood the point raised and so, 
we have attempted to provide an improved definition of pertinent terms and metrics.
To this end, we updated
subsection ``2.3 Motivation and Goal of this Survey'' with revised/re-written 
discussion on the evaluation criteria. We also provided additional examples of
the features we account for in each of the metrics to further clarify their
nature/objective(s).

We believe the revised text to have clarified the issue raised and 
to present a more straightforward reading at this time.

%% R3.C2
\subsubsection*{\textbf{\textsf{Reviewer's Comment\#2}}}
\noindent
\emph{I also recommend looking for potential trends/patterns in P2P overlay network
approaches over time of introducing these approaches. Maybe listing approaches by time
while studying the evaluated metrics.}\\[6pt]

\noindent
\textbf{\textsf{Response}}:
That is a very good point! 
We have updated our manuscript by
creating timeline plots for depicting families of all surveyed approaches 
and elaborated accordingly
in the respective discussion sections.

Specifically, the timeline figures depict algorithms and methodologies. In one hand, we embed
algorithms/papers per year and on the other hand we show which of the characteristic methodologies
are used per surveyed year. We also emphasize when each methodology first appears in the
literature. That way we are capturing the temporal and trending dimensions of the
surveyed material. Moreover, we have updated paragraphs 3.2 and 4.2 (for the unstructured
and structured sections, respectively) by adding discussion points on each of the timeline figures.

\baselineskip=0.95\baselineskip

%% R3.C3 
\subsubsection*{\textbf{\textsf{Reviewer's Comment\#3}}}
\noindent
\emph{On this note, you should add the year next to each examined approach in figures 19-21, 31-33.}\\[6pt]

\noindent
\textbf{\textsf{Response}}:
We have updated the respective figures mentioned by the reviewer to contain a year indication
next to the examined approach.

%% R3.C4 
\subsubsection*{\textbf{\textsf{Reviewer's Comment\#4}}}
\noindent
\emph{I recommend to add the name of each approach to the left of the
``efficiency overhead scalability'' mini-tables, and not only with the tables that have
more than one approach. I also recommend highlighting the name of each approach (in bold)
at the start of each respective paragraph.}\\[6pt]

\noindent
\textbf{\textsf{Response}}:
Mini tables updated and highlighting approach name added as proposed by the reviewer.

%% R3.C5
\subsubsection*{\textbf{\textsf{Reviewer's Comment\#5}}}
\noindent
\emph{Page 2, bottom of left column, ``This research area started to become active after The mismatch problem is Interest ...''}\\[6pt]

\noindent
\textbf{\textsf{Response}}:
Removed the line as it was not supposed to be there. Thank you for pointing this out.

%% R3.C6
\subsubsection*{\textbf{\textsf{Reviewer's Comment\#6}}}
\noindent
\emph{Page 3, first paragraph ``... approximately 80 million songsJupiterMedi...'' insert space after ``songs''}\\[6pt]

\noindent
\textbf{\textsf{Response}}:
Added a space character in the position correctly suggested by the reviewer.

%% R3.C7
\subsubsection*{\textbf{\textsf{Reviewer's Comment\#7}}}
\noindent
\emph{Page 8 in the APS paragraph, 8th line ``The success of THIS approach ...'' (add ``this'')}\\[6pt]

\noindent
\textbf{\textsf{Response}}:
Added the word ``this'' to the respective position.

%% R3.C7
\subsubsection*{\textbf{\textsf{Reviewer's Comment\#7}}}
\noindent
\emph{Page 11, last line, ``Should there BE m landmarks adopted...'' (move ``be'')}\\[6pt]

\noindent
\textbf{\textsf{Response}}:
Moved the verb ``be'' to its correct place in the sentence as pointed out by the reviewer.

\end{document}

### 2015-09-26 acknowledge.tex
2015.09.28 (Alex, Mema & Vassilis) Rephrasing and fixing typos. Adding rebutal letter and new letter to area editor. Including revised (r1) submission. Minor file reorganization and Makefile cleanup.

We would also like to express our gratitude to all the anonymous reviewers who helped us improve the presentation of our work with their insightful comments. This research has been partially supported by \emph{EC FP7 Workprogramme (2007-2013)} under grant agreement n. 283610 \emph{``European Scalable EarthScience Service Environment (EarthServer)''} and \emph{EC H2020} under grant agreement n. 654367 \emph{``Agile Analytics on Big Data Cubes (EarthServer 2)''}.

This  work  has  been  partially  supported  by \emph{SocWeb}, \emph{iMarine}, and \emph{Sucre} \emph{FP7 EU projects}.

>>>>

We would like to thank the anonymous reviewers who helped us 
improve the presentation of our work with their insightful comments. 
This  work  has  been  partially  supported  by
\emph{iMarine} \emph{FP7 EU} project and \emph{ERC Starting Grant n. 279237}.

### 2015-09-26 background.tex
2015.09.28 (Alex, Mema & Vassilis) Rephrasing and fixing typos. Adding rebutal letter and new letter to area editor. Including revised (r1) submission. Minor file reorganization and Makefile cleanup.

Early overlay protocol implementations gave litte attention to the 
topology mismatch problem.
\emph{Gnutella}, for example, is
considered far from scalable~\cite{ritter_gnucantscale_2001} for every peer
chooses its neighbors without any knowledge of the underlying
network, resulting in mismatches. 
Queries are flooded over multiple paths in an effort 
to reach nodes that have the sought content. 
In addition, 
pairs of nodes may simultaneously forward the same query to each other
in a superfluous mode of operation in 
this opportunistic and without coordination environment.
%%
\cite{matei_mapgnutella_2002} showed that, even when $95$\% of any two nodes 
are less than $7$ hops away from each other, 
a \emph{flooding-based} \emph{Gnutella}-like algorithm 
can generate $330$TB/month traffic in a $50,000$ node network. 
A topology mismatch can thus have a serious effect 
on Internet's routing performance.

@@

With \emph{overhead}, we, coarsely, quantify the additional cost a given approach
imposes to the underlying resources when applied to
\begin{inparaenum}[\itshape i\upshape)]
  \item create,
  \item adapt, and
  \item maintain
\end{inparaenum}
the overlay network while preserving its topology awareness. Computing and
communicating peer join and departure, message forwarding, updating routing tables
are some of things that we take into account to perform our assessement. Note
that this is the one criterion of the three we use that its literal values
``low'' and ``high'' must be interpreted as ``better'' and ``worse'' respectivelly.

>>>>

Early overlay protocol implementations gave little attention to the 
topology mismatch problem.
\emph{Gnutella}, for example, is
considered far from scalable~\cite{ritter_gnucantscale_2001} for every peer
chooses its neighbors without any knowledge of the underlying
network, resulting in mismatches. 
Queries are flooded over multiple paths in an effort 
to reach nodes that have the sought content. 
In addition, 
pairs of nodes may simultaneously forward the same query to each other
in a superfluous mode of operation in 
this opportunistic and without coordination environment.
%%
\cite{matei_mapgnutella_2002} showed that, even when $95$\% of any two nodes 
are less than $7$ hops away from each other, 
a \emph{flooding-based} \emph{Gnutella}-like algorithm 
can generate $330$TB/month traffic in a $50,000$ node network. 
A topology mismatch can thus have a serious effect 
on Internet's routing performance.

@@

With \emph{overhead}, we, coarsely, quantify the additional cost a given approach
imposes to the underlying resources when applied to
\begin{inparaenum}[\itshape i\upshape)]
  \item create,
  \item adapt, and
  \item maintain
\end{inparaenum}
the overlay network while preserving its topology awareness. Computing and
communicating peer join and departure, message forwarding, updating routing tables
are some of things that we take into account to perform our assessement. Note
that this is the one criterion of the three we use that its literal values
``low'' and ``high'' must be interpreted as ``better'' and ``worse'' respectively.

### 2015-09-26 conclusion.tex
2015.09.20 (Vassilis) Added acknowledgements section. Updated metric definitions. Introduced timeline figures to capture termoral and trending dimensions of surveyed material. Minor fixes and typos.
2015.09.28 (Alex, Mema & Vassilis) Rephrasing and fixing typos. Adding rebutal letter and new letter to area editor. Including revised (r1) submission. Minor file reorganization and Makefile cleanup.

% TODO: Should be reviewed
\section{Conclusion}
\label{section:conclusion}

%% Removing after Mema's suggestion
%Research and development in applications and systems that follow the 
%\p\ architectural paradigm have flourished for more than a decade now.
%By and large, such artifacts exploit the loose-coupling and self-organization 
%of participating nodes to shape substrates upon which diverse applications 
%can run; the latter offer services including, but not limited to, 
%distributed naming, 
%Internet telephony and video conferencing, 
%storage and indexing, 
%content and file sharing, 
%web crawling and caching, 
%event notification and subscribing/publishing.
%%%
%These services are provided atop the 
%best-effort infrastructure of today's Internet 
%and they have to effectively deal with an array of key quality attributes that
%they may have to offer, such as node availability, robustness,
%scalability, load-sharing, quality-of-service and user anonymity.
%%%
%The difficulty to handle such features effectively, emanates from the fact that
%peer nodes operate at the edge of the Internet and no adequate attention 
%is paid to the structure of the physical network during the 
%network formation at the application-level.
%The deviation of the distributed logically-formed overlay from the 
%physical network yields suboptimal use of the underlying 
%infrastructure and is known as the topology mismatch
%problem.
%
Development of \p--systems and applications
typically involve juggling a set of tradeoffs (e.g.,
choosing higher accuracy at the cost of increased system overhead).
% Computer systems design is typically about juggling a set of tradeoffs (e.g.,
% choosing higher accuracy at the cost of increased system overhead.)  
In surveying more than
a decade's worth of research efforts aimed at solving the topology mismatch
problem in both unstructured and structured \p\ networks, we find this
tussle-of-tradeoffs property to hold.  
With regards to the three criteria we used --efficiency,
overhead, and scalability-- we find that none of the proposed solutions 
is superior to the others on all three fronts.  This is not surprising.
Nonetheless, by
\begin{inparaenum}[\itshape i\upshape)]
  \item presenting an analysis of each of the solutions,
including what distinguishes it from 
others as well as its advantages and disadvantages and 
  \item offering a pictorial
comparison of how each solution fares with regards to others 
as far as
efficiency, overhead, and scalability are concerned,
\end{inparaenum}
we hope to provide \p\
developers and researchers with enough insight and perspective;
as they face specific problems, they will be readily able to 
draw the best possible design decisions for their applications.

>>>>

\section{Conclusion}
\label{section:conclusion}

%% Removing after Mema's suggestion
%Research and development in applications and systems that follow the 
%\p\ architectural paradigm have flourished for more than a decade now.
%By and large, such artifacts exploit the loose-coupling and self-organization 
%of participating nodes to shape substrates upon which diverse applications 
%can run; the latter offer services including, but not limited to, 
%distributed naming, 
%Internet telephony and video conferencing, 
%storage and indexing, 
%content and file sharing, 
%web crawling and caching, 
%event notification and subscribing/publishing.
%%%
%These services are provided atop the 
%best-effort infrastructure of today's Internet 
%and they have to effectively deal with an array of key quality attributes that
%they may have to offer, such as node availability, robustness,
%scalability, load-sharing, quality-of-service and user anonymity.
%%%
%The difficulty to handle such features effectively, emanates from the fact that
%peer nodes operate at the edge of the Internet and no adequate attention 
%is paid to the structure of the physical network during the 
%network formation at the application-level.
%The deviation of the distributed logically-formed overlay from the 
%physical network yields suboptimal use of the underlying 
%infrastructure and is known as the topology mismatch
%problem.
%
Development of \p--systems and applications
typically involve juggling a set of trade-offs (e.g.,
choosing higher accuracy at the cost of increased system overhead).
% Computer systems design is typically about juggling a set of tradeoffs (e.g.,
% choosing higher accuracy at the cost of increased system overhead.)  
In surveying more than
a decade's worth of research efforts aimed at solving the topology mismatch
problem in both unstructured and structured \p\ networks, we find this
tussle-of-trade-offs property to hold.  
With regards to the three criteria we used --efficiency,
overhead, and scalability-- we find that none of the proposed solutions 
is superior to the others on all three fronts.  This is not surprising.
Nonetheless, by
\begin{inparaenum}[\itshape i\upshape)]
  \item presenting an analysis of each of the solutions,
including what distinguishes it from 
others as well as its advantages and disadvantages and 
  \item offering a pictorial
comparison of how each solution fares with regards to others 
as far as
efficiency, overhead, and scalability are concerned,
\end{inparaenum}
we hope to provide \p\
developers and researchers with enough insight and perspective;
as they face specific problems, they will be readily able to 
draw the best possible design decisions for their applications.

### 2015-09-26 intro.tex
2015.09.28 (Alex, Mema & Vassilis) Rephrasing and fixing typos. Adding rebutal letter and new letter to area editor. Including revised (r1) submission. Minor file reorganization and Makefile cleanup.

For over a decade, researchers have extensively investigated  
various aspects of the topology mismatch problem.
The main objective of this paper is to offer a comprehensive 
survey of the work carried out in the area
and provide a
taxonomy of the proposed solutions. We point out synergies, as well as
similarities and differences in the published approaches. 
Ultimately, our goal is to help readers sift through 
the voluminous literature, to help them
understand the advantages and disadvantages of each work, and 
to provide them with enough perspective so that 
when the need arises, they are able to
select, amongst the different approaches, the one that is most suitable for
their particular application.
%%
The rest of the paper is organized as follows: 
In Section~\ref{section:background}, we provide background on
overlay architectures including centralized, decentralized-unstructured and
decentralized-structured \p\ systems.
We also formally define the problem of topology mismatch 
and offer the rationale behind our 
evaluation of the techniques discussed in this paper. 
Work in the area was inspired mostly by the volatile and fully
distributed nature of the decentrilized overlays so we skip
centralized systems and in Sections~\ref{section:unstructured} and~\ref{section:structured}
we outline the surveyed research efforts
for unstructured and structured \p\ overlays, respectively.
We conclude in Section~\ref{section:conclusion}.

>>>>

For over a decade, researchers have extensively investigated  
various aspects of the topology mismatch problem.
The main objective of this paper is to offer a comprehensive 
survey of the work carried out in the area
and provide a
taxonomy of the proposed solutions. We point out synergies, as well as
similarities and differences in the published approaches. 
Ultimately, our goal is to help readers sift through 
the voluminous literature, to help them
understand the advantages and disadvantages of each work, and 
to provide them with enough perspective so that 
when the need arises, they are able to
select, amongst the different approaches, the one that is most suitable for
their particular application.
%%
The rest of the paper is organized as follows: 
In Section~\ref{section:background}, we provide background on
overlay architectures including centralized, decentralized-unstructured and
decentralized-structured \p\ systems.
We also formally define the problem of topology mismatch 
and offer the rationale behind our 
evaluation of the techniques discussed in this paper. 
Work in the area was inspired mostly by the volatile and fully
distributed nature of the decentralized overlays so we skip
centralized systems and in Sections~\ref{section:unstructured} and~\ref{section:structured}
we outline the surveyed research efforts
for unstructured and structured \p\ overlays, respectively.
We conclude in Section~\ref{section:conclusion}.

### 2015-09-26 journals/jss/letter-to-editor/letter-to-editor.tex
2015.09.28 (Alex, Mema & Vassilis) Rephrasing and fixing typos. Adding rebutal letter and new letter to area editor. Including revised (r1) submission. Minor file reorganization and Makefile cleanup.

%% style-specific parameters
\todayis{September 28th, 2015}
\myname{Alex Delis \\ Professor}
\myemail{\url{ad@di.uoa.gr}}
\myweb{\url{www.di.uoa.gr/~ad}}
\myphone{+30-210-727.5212}
\myfax{+30-210-727.5214}
\mycountry{Greece}
\mytitle{}

\begin{document}
\recipient{%
Professor Eleni Karatza \\
Area Editor - \emph{Journal of Systems and Software} \\
Department of Informatics \\
Aristotle University of Thessaloniki \\
54124 Thessaloniki, Greece
}

\begin{letter}{Dear Professor Karatza, }

@@

We are submitting the revision of our paper entitled 
``Alleviating the Topology Mismatch Problem in Distributed Overlay Networks
: A Survey''. We have initially submitted this paper to 
{\it Journal of Systems and Software} on July 21st, 2015.

@@

We also provide specific replies to comments made by the 
two reviewers.

Thank you very much for kindly taking the time to handle our 
revised submission and we look forward to hearing from you.

>>>>

%% style-specific parameters
\todayis{July 21st, 2015}
\myname{Alex Delis \\ Professor}
\myemail{\url{ad@di.uoa.gr}}
\myweb{\url{www.di.uoa.gr/~ad}}
\myphone{+30-210-727.5212}
\myfax{+30-210-727.5214}
\mycountry{Greece}
\mytitle{}

\begin{document}
\recipient{%
Professor Hans van Vliet \\
Editor-in-Chief, \emph{Journal of Systems and Software}\\
Dept. of Computer Science, VU University, \\
De Boelelaan 1081, 1081 HV, \\
Amsterdam, The Netherlands
}

\begin{letter}{Dear Professor van Vliet,}

@@

We are submitting a paper entitled 
``Alleviating the Topology Mismatch Problem in Distributed Overlay Networks
: A Survey''
for consideration 
to the {\it Journal of Systems and Software}.

@@

Thank you very much for kindly taking the time to handle our submission and
we look forward to hearing from you soon.
